### 2020-04-10 serial.tex
slowly making progress...

>>>>

\section{Serial interval distributions}

The serial interval is defined as the time between when an infector becomes symptomatic and when and infectee becomes symptomatic.
We express realized serial intervals as:
\begin{equation}
- x_0 + \sigma + x_1
\end{equation}
where $x_0$ and $x_1$ represent the realized time from infection to symptom onset of an infector and an infectee, respectively, and $\sigma$ represents the realized generation interval.
Previous studies have assumed that (i) $x_0$ and $x_1$ have the same mean and (ii) therefore the serial and generation intervals have the same mean;
however, these results implicitly assume that incidence stays constant.

Using the cohort-based framework provides a clear way of understanding the serial-interval distribution.
Given that an infector became symptomatic at time $\ell$, we have to first go backward in time by asking when the infector was infected and go forward in time by asking when the infectee became symptomatic.
Then, it is clear that $x_0$ should follow the backward incubation period distribution for secondary cohort $\ell$; 
$\sigma$ the forward generation-interval distribution for a primary cohort $\ell - x_0$ conditional on the realized incubation period $x_0$;
and $s_1$ forward incubation period distribution for a primary cohort $\ell - x_0 + \sigma$.
Assuming that the forward incubation distribution does not vary across cohorts, the forward serial interval distribution of a primary cohort $\ell$ can be written as follows:
\begin{equation}
f_\ell(\tau) = \int_{0}^\infty \int_{0}^\infty i(\ell - x_0) h_{\ell - x_0}(x_0, \sigma) k(\tau-\sigma+x_0) d x_0 d\sigma
\end{equation}
where $h$ is the joint probability distribution of the incubation period and generation interval of a primary cohort $\ell - x_0$, and $k$ is a marginal probability distribution describing incubation periods.

Likewise, we can define backward serial interval distribution for a secondary cohort $\ell$.
Given that an infectee became symptomatic at time $\ell$, we have to first go backward in time by asking when the infectee became infected and when the infectee was infected by the infector; 
then, we have to go forward in time by asking when the infector became symptomatic.
In this case, $x_1$ and $\sigma$ follow the backward incubation period and generation-interval distributions, respectively, and $x_0$ follows the forward incubation period distribution.
Therefore, the backward serial interval distribution of a primary cohort $\ell$ can be written as follows
\begin{equation}
f_\ell(\tau) = \int_{0}^\infty \int_{0}^\infty i(\ell - x_0) h_{\ell - x_0}(x_0, \sigma) k(\tau-\sigma+x_0) d x_0 d\sigma
\end{equation}
